Collective excitations in competing phases in two and three dimensions

### 2024-03-26 paper/main.tex
Results 1

\section{Results}\label{sec:results}

In this section, we will be investigating four different diagonal Green's functions $G_{AA^\dagger}(\omega + \im 0^+)$, namely with
\begin{subequations}
    \label{eqn:resolvent_bases}
    \begin{align}
        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right)  
            = \int \dgamma \left( f_{\gamma} + f_{\gamma}^\dagger \right) \,,\\
        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) = \int \dgamma \left( f_{\gamma} - f_{\gamma}^\dagger \right) \,,\\
        A_\text{CDW}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) = \int \dgamma \left( g_{\gamma \up} + g_{\gamma \down} \right) \,,\\
        A_\text{l.AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) = \int \dgamma \left( g_{\gamma \up} - g_{\gamma \down} \right) \,, \\
        A_\text{t.AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( \tau_{\vk} + \tau_{\vk}^\dagger \right) = \int \dgamma \left( \tau_{\gamma \up} + \tau_{\gamma \down} \right) \,,
    \end{align}
\end{subequations}
where $N$ is the number of lattice sites in the system. 
Each one of these operators generates a different kind of collective mode.
The first operator captures the amplitude mode of the $s$-wave superconducting state, while the second one catches the phase mode \cite{Fan22}.
The remaining two capture the collective behavior of the CDW and AFM states, respectively.
In the following, we will refer to the Green's functions generated by these operators as \textcolor{\markEdited}{$\mathcal{G}_{\alpha}(\omega) = G_{A_\alpha A_\alpha^\dagger}(\omega)$ 
with $\alpha \in \{ \text{Higgs}, \text{Phase}, \text{CDW}, \text{l.AFM}, \text{t.AFM} \}$.}

Note, that all of the aforementioned operators are Hermitian. 
This means that all spectral functions need to be completely antisymmetrical \cite{rickayzen80}.%, see appendix \ref{sec:antisymmetry_spectral}.
For this reason, we will only show the $\omega \geq 0$ in our plots. 
Additionally, we will add a small imaginary part of $10^{-5}t$ to $\omega$ in order to visualize the occurring $\delta$ peaks.
\textcolor{\markEdited}{Furthermore, we provide a brief analysis of the effect of choosing different numbers of discretization points $N_\gamma$ in appendix \ref{sec:finite_size}.}

@@

To begin, let us describe the spectral functions $\mathcal{A}_\alpha (\omega) = - (1/\pi) \Im [\mathcal{G}_\alpha (\omega + \im 0^+)]$ with respect to the operators above in the various phases.
\autoref{fig:resolvent_overview_SC} shows them at $U = -2.5t$ in the SC ($V=-0.1t$) and CDW ($V=0.1t$ and $V=0.5t$) phase.

There are a variety of different features. The difference between the two lattices is mostly quantitative.
First and foremost, in the SC phase, see panel (a), 
there is a sharp peak located at $\omega=0$ in $\spectral{Phase}$ and a singularity in $\spectral{Higgs}$ located at $\omega=2\Delta_\text{SC}$.
We identify them with the well-known Anderson-Bogoliubov and Higgs modes in superconductors \cite{Bogoljubov1958,Anderson58,Brieskorn74,Schmid1975,simanek1975,schoen1976propagating,Kulik1981,Maiti2015,Sun2020,Fan22,Schmid1975,Varma02,Cea14,Measson14,Tsuji15,Krull16,Mueller2019,Schwarz20}.
Note, that the former must not have any weight though, because the spectral function is perfectly antisymmetrical.
The peak itself can be found at zero energy because our model describes a neutral superfluid 
wherein there is no coupling of the phase of the order parameter to the electromagnetic potential.
Therefore, this phase may be chosen arbitrarily, and changing it requires no energy 
which ultimately allows a Goldstone mode to exist in the first place \cite{Goldstone1961,Anderson63}.

To characterize the occurring peaks that lie outside the two-particle continuum, we turn towards the real part of the Green's function.
We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly $y = ax + b$ to obtain its power-law behavior.
The real part is related to the imaginary part via the Kramers-Kronig relations.
Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e., $a=-1$, and the peak has the weight $W_0 = \exp(b)$.
Furthermore, an exponent of $a=-2$ corresponds to the derivative of the $\delta$ distribution, i.e., $\delta'(\omega)$.
The fits themselves can be found in appendix \ref{sec:fit_greens_functions}.

This analysis provides that the real part of $\greens{Phase}$ near $\omega=0$ behaves as $1/\omega^2$ indicating that the peak in $\spectral{Phase}$ is the derivative of a $\delta$ distribution.
The weight of such a peak is given by the integral $\int \delta'(\omega) \mathrm{d}\omega = 0$.
This confirms our previous expectation that this peak cannot have any weight.

The singularity in $\spectral{Higgs}$ behaves as $1/\sqrt{\omega - 2 \Delta_\text{SC}}$.
Previous studies on the dynamics of the order parameter found damped oscillations after a quench.
These have the frequency $\Omega = 2 \Delta_\text{SC}$ and fall off as $1/\sqrt{t}$ \cite{Volkov73,Kulik1981,Yuzbashyan06}.
An inverse Fourier transform of $\spectral{Higgs}$ yields precisely the same behavior, thereby reinforcing the validity of our results.

In the CDW phase, see panels (b) and (c), both of $\spectral{Higgs}$ and $\spectral{Phase}$ become identical and form a $\delta$ peak below the two-particle continuum.
\textcolor{\markEdited}{In this case, both modes describe the condensation of a cooperon, i.e., a bound state of two electrons.}
Following the Landau theory for continuous phase transitions, this is to be expected as the free energy is expanded in terms of the order parameter as
\begin{equation}
    f(\Delta_\text{SC}) \approx r |\Delta_\text{SC}|^2 + \frac{u}{2} |\Delta_\text{SC}|^4\,,
\end{equation}
with $r > 0$ and $u > 0$ if the system is outside of the superconducting phase. 
In this case, the only minimum is at $\Delta_\text{SC} = 0$ \cite{Coleman2015}. 
That means that both possible modes have to overcome the same energy to be excited at all.

In the SC phase, $\spectral{CDW}$ features a $\delta$ peak below the continuum corresponding to the finite energy necessary to excite this kind of electronic density modulation.
\textcolor{\markEdited}{This mode corresponds to the creation of an exciton.}
For moderate-sized values of $V>0$, i.e., in the CDW phase, see panel (b) at $V=0.1t$, the aforementioned spectral function has a singularity at $\omega=2\Delta_\text{CDW}$.% that exhibits a square-root behavior.
\textcolor{\markEdited}{This mode moves out of the two-particle continuum as $V$ is increased and becomes a proper $\delta$ peak, see panel (c) at $V=0.5t$.}

\textcolor{\markEdited}{$\spectral{t.AFM}$ and $\spectral{l.AFM}$ are identical and restricted to the continuum for both phases and both lattices.
The former statement can be understood by the same argument why $\spectral{Phase}$ and $\spectral{Higgs}$ are identical outside of the SC phase:
If no AFM order is present, the same amount of energy is required to create any such excitation, in this case, a magnon.}
For the square lattice, there is a singularity located at the upper edge of the two-particle continuum.

@@

At $V=0$, both the SC and the CDW orders coexist. 
In this phase, the mean-field single-particle energies are given by
\begin{equation}
    E_{\pm} = \pm \sqrt{\epsilon^2 + |\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}\,.
\end{equation}
This means that the proper order parameter is $\Delta_\text{tot} \coloneqq \sqrt{|\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}$.
Here, $\Delta_\text{CDW}$ and $\Delta_\text{SC}$ can change arbitrarily without affecting the system's energy as long as $\Delta_\text{tot}$ remains constant.
Note, that the degeneracy of both phases is exact due to the SO(4) symmetry \cite{yang90}.

In \autoref{fig:resolvent_overview_V0}, we show the spectral functions for $U=-2.5t$ and $V=0$.
The different panels correspond to different choices for $\Delta_\text{CDW}$ and $\Delta_\text{SC}$.
First, in panel (a), we set $\Delta_\text{CDW} = 0$.
This results in a purely superconducting phase with the same features as in \autoref{fig:resolvent_overview_SC} panel (a).
\textcolor{\markEdited}{The peak in $\spectral{CDW}$ moves to $\omega=0$. In fact, $\spectral{CDW}$ and $\spectral{Phase}$ are identical.}

Secondly, panel (b) shows the spectral functions for $\Delta_\text{SC} = 0$, i.e., in a purely charge-ordered phase.
Similar to before, there is not much change compared to \autoref{fig:resolvent_overview_SC} panel (b).
The spectral functions $\spectral{Higgs}$ and $\spectral{Phase}$ are still identical, however, both exhibit a sharp peak at $\omega=0$.
This peak is described by $\delta'(\omega)$.

Lastly, we chose $\Delta_\text{CDW} = \Delta_\text{SC}$ for panel (c).
For this specific ratio of $\Delta_\text{CDW}$ and $\Delta_\text{SC}$, $\spectral{Higgs}$ and $\spectral{CDW}$ are identical.
Choosing a different ratio yields qualitatively the same results, but the peaks differ in magnitude.
Both spectral functions have a peak at $\omega = 0$, described by $\delta'(\omega)$, and a singularity at the lower edge of the two-particle continuum $\omega = 2\Delta_\text{tot}$.
Each one of the singularities behaves as $1/\sqrt{\omega - 2 \Delta_\text{tot}}$.
\textcolor{\markEdited}{Essentially, varying the ratio of the two gap parameters smoothly switches $\spectral{Higgs}$ and $\spectral{CDW}$.}

\textcolor{\markEdited}{We associate the peak in the amplitude-related spectral functions at $\omega=0$ with this shifting of order parameters, i.e., diminishing one and increasing the other while keeping $\Delta_\text{tot}$ constant.
Specifically, in the pure SC phase, we find this peak only in $\spectral{CDW}$.
This can be understood as follows: The operator $A_\text{CDW}$ in \eqref{eqn:resolvent_bases} creates an exciton and thereby increases $|\Delta_\text{CDW}|$.
This can in essence be achieved without any external energy by lowering $\Delta_\text{SC}$.
However, the converse is not true: Since $\Delta_\text{CDW}$ is already 0, creating another Cooper pair by virtue of $A_\text{Higgs}$ will always increase $\Delta_\text{tot}$ and therefore requires a minimum energy of $2 \Delta_\text{tot}$.
The same argument can be made for the pure CDW phase.
If, however, both orders are present, the system can shift between them arbitrarily by creating either kind of excitation.
Hence, in this case, we find a peak at $\omega=0$ in both spectral functions.}

$\spectral{Phase}$ behaves just as it does in the pure SC phase. It has only a peak at $\omega = 0$ that can be associated with the change of the phase of $\Delta_\text{SC}$.

@@

Lastly, we investigate the same spectral functions close to the AFM-CDW phase transition, depicted in \autoref{fig:resolvent_overview_AFM}.
\textcolor{\markEdited}{We choose $V=1.2t$ for the square lattice and $V=0.8t$ for the simple cubic lattice.
This yields that the phase transition is located at $U=4.8t$ for both cases. 
The panels (a) and (b) show the system close to the phase transition at $U=4.8t \pm 0.1t$.}
Again, both SC-related spectral functions are identical in both the CDW and AFM phases.
Within the continuum their weight is shifted towards the upper edge and on the square lattice only, there is a peak above the continuum.
In the AFM phase, both $\spectral{l.AFM}$ and $\spectral{CDW}$ have a peak close, but yet below, the two-particle continuum.
The peak of the former is at a lower energy than the peak of the latter.
In the CDW phase, this behavior is reversed, i.e., the peak in $\spectral{CDW}$ lies lower.
Using the same analysis as before, we conclude that each of these peaks is a $\delta$ peak.
\textcolor{\markEdited}{Moving further away from the phase transition, here $U=4.8t \pm 1.4t$ in panels (c) and (d), the upper peak moves into the two-particle continuum while the other one persists.
Both close and far away from the phase transition, but only in the AFM phase, $\spectral{t.AFM}$ exhibits a $\delta'$ peak at $\omega=0$.
This represents a transversal magnon and is the Goldstone boson for the AFM phase.}

>>>>

\section{Results}
\label{sec:results}

We investigate four different diagonal Green's functions $G_{AA^\dagger}(\omega + \im 0^+)$ with
\begin{subequations}
    \label{eqn:resolvent_bases}
    \begin{align}
        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right)  
            = \int_{-1}^1 \dgamma \left( f_{\gamma} + f_{\gamma}^\dagger \right) ,\\
        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) = 
				\int_{-1}^1 \dgamma \left( f_{\gamma} - f_{\gamma}^\dagger \right) ,\\
        A_\text{CDW}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) = 
				\int_{-1}^1 \dgamma \left( g_{\gamma \up} + g_{\gamma \down} \right) ,\\
        A_\text{l.AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) = 
				\int_{-1}^1 \dgamma \left( g_{\gamma \up} - g_{\gamma \down} \right) , \\
        A_\text{t.AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( \tau_{\vk} + \tau_{\vk}^\dagger \right) = 
				\int_{-1}^1 \dgamma \left( \tau_{\gamma \up} + \tau_{\gamma \down} \right) ,
    \end{align}
\end{subequations}
where $N$ is the number of lattice sites in the system. 
Each of these operators generates a different kind of collective mode.
The first operator excites the amplitude mode of the $s$-wave superconducting state
while the second one excites the phase mode \cite{Fan22}.
The remaining two operators induce the collective behavior of the CDW and AFM order, respectively.
This means these Green's functions are the susceptibilities towards alternating local potential (CDW) or
alternating magnetic field (AFM).
Below, we refer to the Green's functions of these operators by
$\mathcal{G}_{\alpha}(\omega) = G_{A_\alpha A_\alpha^\dagger}(\omega)$ 
with $\alpha \in \{ \text{Higgs}, \text{Phase}, \text{CDW}, \text{l.AFM}, \text{t.AFM} \}$.
Furthermore, we use $\text{SC}$ when the Higgs and phase mode yield the same spectral function and
$\text{AFM}$ when longitudinal and transversal magnons yield the same spectral function.

The operators in \eqref{eqn:resolvent_bases} are Hermitian and of bosonic character. 
This means that all spectral functions are antisymmetric \cite{rickayzen80}.
For this reason, we only show the part  $\omega \geq 0$ in our plots. 
Additionally, we add a small positive imaginary part of $10^{-5}t$ to $\omega$ 
in order to plot the $\delta$ peaks as Lorentzians.
We analyze the effect of different numbers of sampling points $N_\gamma$ in App.\ \ref{sec:finite_size}.

@@

Let us describe the spectral functions 
$\mathcal{A}_\alpha (\omega) = - (1/\pi) \Im [\mathcal{G}_\alpha (\omega + \im 0^+)]$ of
the operators above in the various phases.
Fig.\ \ref{fig:resolvent_overview_SC} shows them at $U = -2.5t$ in the SC ($V=-0.1t$) and  in the 
CDW ($V=0.1t$ and $V=0.5t$) phase.

There are a variety of different features. 
The results for the lattices in 2D and 3D are very similar and differ only quantitatively.
In the SC phase, see Fig.\ \ref{fig:resolvent_overview_SC}(a), 
there is a sharp peak located at $\omega=0$ in $\spectral{Phase}$ and a 
singularity in $\spectral{Higgs}$ located at $\omega=2\Delta_\text{SC}$.
We identify them with the well-known Anderson-Bogoliubov mode and Higgs mode, respectively, in superconductors 
\cite{Bogoljubov1958,Anderson58,Brieskorn74,Schmid1975,simanek1975,schon76,Kulik1981,Maiti2015,Sun2020,Fan22,Schmid1975,Varma02,Cea14,Measson14,Tsuji15,Krull16,Mueller2019,Schwarz20}.
The former must not have any weight because of the antisymmetry of the spectral function.
The peak itself is located at zero energy because the model \eqref{eqn:full_hamiltonian} 
describes a neutral superfluid without coupling of the phase of the order parameter to the electromagnetic fields.
Therefore, this phase may be chosen arbitrarily, and changing it requires no energy 
which ultimately induces a Goldstone mode to exist \cite{Goldstone1961,Anderson63}.

To characterize the occurring peaks that lie outside the two-particle continuum, we inspect the real part of the Green's function.
We plot it in the vicinity of the peaks with a double logarithmic scale and fit 
the result linearly $y = ax + b$ to obtain its power-law behavior.
The real part is related to the imaginary part via the Kramers-Kronig relations.
Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e., $a=-1$, and the peak has the weight $W_0 = \exp(b)$.
Furthermore, an exponent of $a=-2$ corresponds to the 
derivative of the $\delta$ distribution, i.e., $\delta'(\omega)$.
The fits themselves are given in App.\ \ref{sec:fit_greens_functions}.

This analysis yields that the real part of $\greens{Phase}$ near $\omega=0$ behaves like
$1/\omega^2$ showing that the peak in $\spectral{Phase}$ is the derivative of a $\delta$ distribution.
The weight of such a peak is given by the integral $\int \delta'(\omega) \mathrm{d}\omega = 0$ and thus
vanishes in accordance with expectations.

The singularity in $\spectral{Higgs}$ behaves like $1/\sqrt{\omega - 2 \Delta_\text{SC}}$.
Previous studies on the dynamics of the order parameter found dephasing oscillations after a quench.
These oscillations have the frequency $\Omega = 2 \Delta_\text{SC}$ and fall off like
$1/\sqrt{t}$ \cite{Volkov73,Kulik1981,Yuzbashyan06}.
An inverse Fourier transform of $\spectral{Higgs}$ yields precisely this behavior, 
thereby corroborating our results.

In the CDW phase, see panels (b) and (c) of Fig.\ \ref{fig:resolvent_overview_SC},
both spectral functions $\spectral{Higgs}$ and $\spectral{Phase}$ become identical and display a $\delta$ peak below the two-particle continuum.
In this case, both modes describe a cooperon, i.e., a bound state of two electrons or two holes.
Following the Landau theory for continuous phase transitions, it is to be expected 
that both excitations show the same spectral behavior. 
If the free energy is expanded in powers of the order parameter 
\begin{equation}
    f(\Delta_\text{SC}) \approx r |\Delta_\text{SC}|^2 + \frac{u}{2} |\Delta_\text{SC}|^4,
\end{equation}
with  $u > 0$. For $r<0$, the system is in the SC phase and $\Delta_\text{SC}$ is finite.
Then it makes a difference if one excites \emph{along} $\Delta_\text{SC}$ in the complex plane (Higgs mode)
or \emph{perpendicular} to it (phase mode). For $r>0$, however, the order vanishes, $\Delta_\text{SC}=0$,
and no distinction between Higgs and phase mode can be made \cite{Coleman2015}. 
Both possible excitation processes have to overcome the same energy.

In the SC phase, $\spectral{CDW}$ features a $\delta$ peak below the continuum corresponding to the finite energy necessary to excite the electronic density modulation of CDW type.
This mode corresponds to the creation of an exciton since it results from a bilinear operator with
creation and annihilation fermionic operator so that it represents a bound electron-hole pair.
For moderate values of $V>0$, i.e., in the CDW phase, see panel (b) at $V=0.1t$, the CDW spectral function 
shows a singularity at $\omega=2\Delta_\text{CDW}$.
This mode moves out of the two-particle continuum upon increasing $V$ 
and becomes a proper $\delta$ peak, see panel (c) of Fig.\ \ref{fig:resolvent_overview_SC} at $V=0.5t$.

The spectral functions $\spectral{t.AFM}$ and $\spectral{l.AFM}$ are identical and restricted to 
the continuum for both phases and both lattices.
This can be understood by the same argument used for the identity of 
$\spectral{Phase}$ and $\spectral{Higgs}$ outside of the SC phase:
If no AFM order is present, there is no distinction between a longitudinal and a transversal excitation. 
The same amount of energy is required to create any such excitation which is a magnon
or paramagnon if there is no long-range AFM order.
For the square lattice, there is a singularity located at the upper edge of the two-particle continuum.
But this does not occur in the 3D case. Including lifetime effects, sharp features at the upper
edge of the continuum are expected to be smeared out anyway.

@@

At $V=0$, the SC and the CDW order can coexist due to the SO(4) symmetry. 
In this phase, the mean-field single-particle energies are given by
\begin{equation}
    E_{\pm} = \pm \sqrt{\epsilon^2 + |\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}.
\end{equation}
This means that the proper order parameter is $\Delta_\text{tot} 
\coloneqq \sqrt{|\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}$.
Here, $\Delta_\text{CDW}$ and $\Delta_\text{SC}$ can change arbitrarily without affecting the system's energy as long as $\Delta_\text{tot}$ remains constant.
This degeneracy of both phases is rigorously exact due to the SO(4) symmetry \cite{yang90}.

In Fig.\ \ref{fig:resolvent_overview_V0}, we show the spectral functions for $U=-2.5t$ and $V=0$.
The different panels correspond to different choices for $\Delta_\text{CDW}$ and $\Delta_\text{SC}$.
First, in panel (a), we set $\Delta_\text{CDW} = 0$.
This results in a purely superconducting phase with the same features as in 
Fig.\ \ref{fig:resolvent_overview_SC}(a).
The peak in $\spectral{CDW}$ moves to $\omega=0$ because it does not cost energy to enhance the CDW order parameter
if it is compensated by a reduction of the SC order parameter. 
In fact, $\spectral{CDW}$ and $\spectral{Phase}$ are identical since they are linked by the SO(4) symmetry.

Second, panel (b) shows the spectral functions for $\Delta_\text{SC} = 0$, i.e., in a purely charge-ordered phase.
Similar to before, there is not much change compared to Fig.\ \ref{fig:resolvent_overview_SC}(b).
The spectral functions $\spectral{Higgs}$ and $\spectral{Phase}$ are still identical since no
SC order is present. Both exhibit a sharp peak at $\omega=0$ proportional to $\delta'(\omega)$
which reflects that an SC order can be introduced without energy cost if compensated by a reduction of the CDW order.

Last, we choose $\Delta_\text{CDW} = \Delta_\text{SC}$ in panel (c).
For this specific ratio of $\Delta_\text{CDW}$ and $\Delta_\text{SC}$, 
$\spectral{Higgs}$ and $\spectral{CDW}$ are identical.
Choosing a different ratio yields qualitatively the same results, but the peaks differ in magnitude.
Both spectral functions have a peak at $\omega = 0$ proportional to $\delta'(\omega)$
and a singularity at the lower edge of the two-particle continuum $\omega = 2\Delta_\text{tot}$.
These singularities behave like $1/\sqrt{\omega - 2 \Delta_\text{tot}}$.
Varying the ratio of the two gap parameters allows one to
switch between $\spectral{Higgs}$ and $\spectral{CDW}$ continuously.

We attribute the peak in the amplitude spectral functions at $\omega=0$ 
to the freedom to vary the order parameters, i.e., 
diminishing one and increasing the other while keeping $\Delta_\text{tot}$ 
constant so that the system stays in its ground states. 
In the pure SC phase, we find this peak only in $\spectral{CDW}$.
This can be understood as follows: The operator $A_\text{CDW}$ in \eqref{eqn:resolvent_bases} 
creates an exciton and thereby increases $|\Delta_\text{CDW}|$.
This can be achieved without increasing the energy by lowering $\Delta_\text{SC}$.
However, the reversed argument is not true: Since $\Delta_\text{CDW}$ is already 0, 
creating another Cooper pair by virtue of $A_\text{Higgs}$ always increases $\Delta_\text{tot}$ and thus 
requires a minimum energy of $2 \Delta_\text{tot}$.
The analogous argument holds for the pure CDW phase.
If, however, both orders are present, the system can shift between them arbitrarily 
by creating either kind of excitation.
Hence, in this case, we find a peak at $\omega=0$ in both spectral functions.

The spectral function $\spectral{Phase}$ behaves as it does in the pure SC phase. 
It has only a peak at $\omega = 0$ that is associated with the freedom of choice
of the phase of $\Delta_\text{SC}$.

@@

Finally, we investigate the same spectral functions close to the AFM-CDW phase transition
as depicted in Fig.\ \ref{fig:resolvent_overview_AFM}.
We choose $V=1.2t$ for the square lattice and $V=0.8t$ for the simple cubic lattice so that
the phase transition is located at $U=4.8t$ in both cases. 
The panels (a) and (b) show the system close to the phase transition at $U=4.8t \pm 0.05t$.
Again, the SC-related spectral functions are identical in the CDW and the AFM phases
due to the absence of a finite SC order.
Within the continuum, their weight is shifted towards the upper edge.
On the square lattice only, there is a peak above the continuum.
It is likely to be smeared out if lifetime effects were included.
In the AFM phase, both $\spectral{l.AFM}$ and $\spectral{CDW}$ have a peak close to, but yet below, the two-particle continuum. 
The peak of the former is at a lower energy than the peak of the latter.
In the CDW phase, this behavior is reversed, i.e., the peak of $\spectral{CDW}$ lies lower
than the one in $\spectral{l.AFM}$.
Analyzing the power-law behavior of the real part described above, see also
App.\ \ref{sec:fit_greens_functions}, we confirm that these peaks are $\delta$ peaks.
Moving further away from the phase transition, here $U=6.2t$ in panels (c) \blue{and $U=3.4t$ in panels(d)}
\red{Im Text war (d) benannt, aber das existiert ja nicht.}, 
the upper peak merges with the two-particle continuum while the lower one persists.
We emphasize that the spectral function of the transverse magnon $\spectral{t.AFM}$ always 
displays a $\delta'$ peak at $\omega=0$, independent of how far away the parameters are chosen
from the phase transition. This is the expected behavior of a Goldstone boson.
